GAs Conclusion

### 2022-04-20 graphs_newt_snakes/GAs_conclusion.Rmd
cool animations

lit_30_file<-read.csv(lit_30[1], header = TRUE)
replica <- unlist(str_split(unlist(str_split(lit_30[1],"rep_"))[3], "_"))[1]
lit_30_file$rep<-replica
lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_rate_"))[2], "_"))[1]
lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_rate_"))[2], "_"))[1]
lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
lit_30_file$sim <-"A"

lit_30_G2_file<-read.csv(lit_30_G2[1], header = TRUE)
replica <- unlist(str_split(unlist(str_split(lit_30_G2[1],"rep_"))[3], "_"))[1]
lit_30_G2_file$rep<-replica
lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]

lit_30_G2_file$sim <-"A"

oldstand=0
letter=1
for(i in seq(1, length(lit_30_G2), 1)){
  stand <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  if (stand!=oldstand){
    oldstand=stand
    letter = letter + 1
  }

  GA2_lit_temp_file <- read.csv(lit_30_G2[i], header = TRUE)
  GA2_lit_temp_file$sim <-LETTERS[letter]
  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30_G2[i],"rep_"))[3], "_"))[1]
  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]

@@

  if (i<=length(lit_30)){
  cor_temp_file <- read.csv(lit_30[i], header = TRUE)
  cor_temp_file$sim <-LETTERS[letter]
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  lit_30_file <- rbind(lit_30_file, cor_temp_file)
  rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]

@@

lit_30_file$snake <- paste0(lit_30_file$snake_mu_rate, "_",lit_30_file$snake_mu_effect_sd)
lit_30_file$newt_snake <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd)
lit_30_file$sim
#params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
#params$newt_snake <- paste0(params$newt, "_", params$snake)

lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5350),]
p <- lit_30_file_min %>%
  plot_ly(
    x = ~Newt_pop_size, 
    y = ~Snake_pop_size, 
    color = ~factor(sim), 
    #shape = ~factor(newt)
    frame = ~generation, 
    #text = ~country, 
    #hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  ) %>%
  layout(
    xaxis = list(
      type = "log"
    )
  )

>>>>

lit_30_file<- data.frame()
# 
# lit_30_file<-read.csv(lit_30[1], header = TRUE)
# replica <- unlist(str_split(unlist(str_split(lit_30[1],"rep_"))[3], "_"))[1]
# lit_30_file$rep<-replica
# lit_30_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_rate_"))[2], "_"))[1]
# lit_30_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_rate_"))[2], "_"))[1]
# lit_30_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"snake_mu_effect_sd_"))[2], "_"))[1]
# lit_30_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[1],"newt_mu_effect_sd_"))[2], "_"))[1]
# lit_30_file$sim <-"A"

# lit_30_G2_file<-read.csv(lit_30_G2[1], header = TRUE)
# replica <- unlist(str_split(unlist(str_split(lit_30_G2[1],"rep_"))[3], "_"))[1]
# lit_30_G2_file$rep<-replica
# lit_30_G2_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_rate_"))[2], "_"))[1]
# lit_30_G2_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_rate_"))[2], "_"))[1]
# lit_30_G2_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"snake_mu_effect_sd_"))[2], "_"))[1]
# lit_30_G2_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[1],"newt_mu_effect_sd_"))[2], "_"))[1]
# 
# lit_30_G2_file$sim <-"A"

lit_30_G2_file <- data.frame()
oldstand=0
letter=0
newt_unique=0
newt_numb = 0
for(i in seq(1, length(lit_30_G2), 1)){
  stand <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  up <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  phrase = paste0(stand, "_", up)
  if (stand!=oldstand){
    oldstand=stand
    letter = letter + 1
  }

    if (phrase=="1.0e-08_0.05" ){
    newt_numb =  1
   }
    if (phrase=="1.0e-09_0.158114"){
    newt_numb =  2
   }
      if (phrase=="1.0e-10_0.5"){
    newt_numb =  3
   }
    if (phrase=="1.0e-11_1.58114"){
    newt_numb =  4
   }

      if (phrase=="1.0e-12_5.0"){
    newt_numb =  5
   }

  GA2_lit_temp_file <- read.csv(lit_30_G2[i], header = TRUE)
  GA2_lit_temp_file$sim <-LETTERS[letter]
   GA2_lit_temp_file$size <-newt_numb
  GA2_lit_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30_G2[i],"rep_"))[3], "_"))[1]
  GA2_lit_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_rate_"))[2], "_"))[1]
  GA2_lit_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  GA2_lit_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30_G2[i],"newt_mu_effect_sd_"))[2], "_"))[1]

@@

  if (i<=length(lit_30)){

  stand <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
  up <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  phrase = paste0(stand, "_", up)

   if (phrase=="1.0e-08_0.005"){
    newt_numb =  1
   }
    if (phrase=="1.0e-09_0.05"){
    newt_numb =  2
   }
      if (phrase=="1.0e-10_0.5"){
    newt_numb =  3
   }
    if (phrase=="1.0e-11_5.0"){
    newt_numb =  4
   }

  cor_temp_file <- read.csv(lit_30[i], header = TRUE)
  cor_temp_file$sim <-LETTERS[letter]
  cor_temp_file$size <-newt_numb
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(lit_30[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  lit_30_file <- rbind(lit_30_file, cor_temp_file)
  rep <-unlist(str_split(unlist(str_split(lit_30[i],"rep_"))[3], "_"))[1]

@@

#lit_30_file$sim
lit_30_file$snake <- paste0(lit_30_file$snake_mu_rate, "_",lit_30_file$snake_mu_effect_sd)
lit_30_file$newt <- paste0(lit_30_file$newt_mu_rate, "_",lit_30_file$newt_mu_effect_sd)

lit_30_file$newt_snake_rep <- paste0(lit_30_file$newt_mu_rate, "_", lit_30_file$newt_mu_effect_sd, "_", lit_30_file$snake_mu_rate, "_", lit_30_file$snake_mu_effect_sd, "_", lit_30_file$rep)

unique(lit_30_G2_file$snake)
#params$newt_snake <- paste0(params$newt, "_", params$snake)

lit_30_file_min<-lit_30_file[which(lit_30_file$generation>=5000 & lit_30_file$generation<=5550),]
p <- lit_30_file_min %>%
  plot_ly(
    x = ~Newt_pop_size, 
    y = ~Snake_pop_size, 
    color = ~factor(snake), 
    size = ~size,
    frame = ~generation, 
    text = ~factor(newt_snake_rep), 
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  ) %>%
  layout(
    xaxis = list(
      type = "log"
    )
  )

p

lit_30_G2_file$snake <- paste0(lit_30_G2_file$snake_mu_rate, "_",lit_30_G2_file$snake_mu_effect_sd)

lit_30_G2_file$newt <- paste0(lit_30_G2_file$newt_mu_rate, "_",lit_30_G2_file$newt_mu_effect_sd)

lit_30_G2_file$newt_snake_rep <- paste0(lit_30_G2_file$newt_mu_rate, "_", lit_30_G2_file$newt_mu_effect_sd, "_", lit_30_G2_file$snake_mu_rate, "_", lit_30_G2_file$snake_mu_effect_sd, "_", lit_30_G2_file$rep)

lit_30_G2_file_mini<-lit_30_G2_file[which(lit_30_G2_file$generation>=0 & lit_30_G2_file$generation<=5000),]
p <- lit_30_G2_file_mini %>%
  plot_ly(
    x = ~Newt_pop_size, 
    y = ~Snake_pop_size, 
    color = ~factor(sim), 
    #shape = ~factor(newt)
    frame = ~generation, 
    text = ~factor(sim), 
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  ) %>%
  layout(
    xaxis = list(
      type = "log"
    )
  )
